
---
title: "rSPDE Package"
author: "David Bolin and Alexandre B. Simas"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{rSPDE Package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

set.seed(1)
```

```{r inla_link, include = FALSE}
inla_link <- function() {
  sprintf("[%s](%s)", "`R-INLA`", "https://www.r-inla.org")
}
```

# Package Home Page

For more details on the package, along with a brief introduction, function references and several vignettes, go to the [`rSPDE` home page](https://davidbolin.github.io/rSPDE/).

For the source codes, reporting issues, etc., please go the the [`rSPDE` GitHub page](https://github.com/davidbolin/rSPDE).

# Vignettes

For an introduction to the `rSPDE` package, see the vignette:  
[An introduction to the rSPDE package](https://davidbolin.github.io/rSPDE/articles/rSPDE.html).

All other vignettes covering different examples and applications of the package are available at:  
[https://davidbolin.github.io/rSPDE/articles/](https://davidbolin.github.io/rSPDE/articles/).

# Function Manuals

Detailed references for functions including several examples can be found in the [Function References](https://davidbolin.github.io/rSPDE/reference/index.html).
